Analysis for Performing-Articulation performances (DURATION)

### 2020-04-23 material/analysis/expression/stim_a/ioi_duration.Rmd
rescale y axis for seq plot
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

#### Sequence plot
#### Legato
```{r duration_seq_leg, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_duration$TrialNr <- as.factor(dt_duration$TrialNr)
duration_seq <- dt_duration[Subcomponent == "Legato", .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr, RowNr)]

p_duration_seq_leg <- ggplot(data = duration_seq, aes(x = RowNr, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Normalised Duration", subtitle = "Duration: Performing-Articulation(Legato)") +
  scale_x_continuous(breaks=seq(1,66,1))
p_duration_seq_leg
```

@@

#### Staccato
```{r duration_dis_sta, fig.width = 12, echo = FALSE}
p_duration_dis_sta <- ggplot(dt_duration[Subcomponent == "Staccato"], aes(x = normDu)) +
  geom_histogram(binwidt = .1, alpha = .5, position="identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised Duration", y = "Count", subtitle = "Duration: Performing-Articulation(Staccato)")
p_duration_dis_sta
```

>>>>

### Sequence plot
#### All
```{r duration_seq, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_duration$TrialNr <- as.factor(dt_duration$TrialNr)
duration_seq <- dt_duration[Subcomponent != "NA", .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr, RowNr)]

duration_seq_stim_n <- fread("../../stim_n/seq.csv", header = T, sep = ",", dec = ".")
duration_seq_stim_n$SubNr <- factor(duration_seq_stim_n$SubNr)
duration_seq_stim_n$TrialNr <- factor(duration_seq_stim_n$TrialNr)
duration_seq_stim_n$TrialNr <- "Practice"

duration_seq <- rbind(duration_seq, duration_seq_stim_n)

p_duration_seq <- ggplot(data = duration_seq, aes(x = RowNr, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Normalised Duration", subtitle = "Duration: Performing-Articulation(All)") +
  scale_x_continuous(breaks=seq(1,66,1)) + scale_y_continuous(breaks=seq(0,2,0.5), limits = c(0, 2))
p_duration_seq
```

#### Legato
```{r duration_seq_leg, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_duration$TrialNr <- as.factor(dt_duration$TrialNr)
duration_seq_leg <- dt_duration[Subcomponent == "Legato", .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr, RowNr)]

p_duration_seq_leg <- ggplot(data = duration_seq_leg, aes(x = RowNr, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Normalised Duration", subtitle = "Duration: Performing-Articulation(Legato)") +
  scale_x_continuous(breaks=seq(1,66,1))
p_duration_seq_leg
```

@@

#### Staccato
```{r duration_dis_sta, fig.width = 12, echo = FALSE}
p_duration_dis_sta <- ggplot(dt_duration[Subcomponent == "Staccato"], aes(x = normDu)) +
  geom_histogram(binwidth = .1, alpha = .5, position="identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised Duration", y = "Count", subtitle = "Duration: Performing-Articulation(Staccato)")
p_duration_dis_sta
```
